Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-03 article/ms.tex
Altered the method, adding the additional filter we ran and redoing the section on the work of Ho2017.

This study, which queries 450000ish LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed. 190 strong candidates for this signature, almost all of them not at this time associated with any globular cluster, are detailed in Table [REFERENCE TABLE HERE]. These stars occur at a wide range of metalicities, including solar metalicity. The implications for theories attempting to explain the origin of this signiature first found in NGC 2419 is likely to be significant, as for such a theory to be complete, it must now account not only for the stars in the metal poor NGC 2419, but also these stars existing at a range of metalicities in the galactic plane. Further, the task of explaining the uniqueness of NGC 2419 is not removed, as it remains the only globular cluster to significantly display this phenomena.

@@

\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017} using APOGEE data, was fitted to each star in our 450000 star sample of LAMOST giants.
%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to to lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
This model is treated as representative of the expected spectra for each star.

The residuals were taken of the normalised LAMOST flux data and 
\textit{The Cannon} according to $residual=data-model$. A positive residual implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected. In turn, at a given spectral line a lower normalised flux is associated with an over-abundance, while a higher normalised flux is associated with a depleted abundance.

@@

Two filters were applied separately, with the candidate pool formed from all unique stars identified in either filter. The first, broader filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$. The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the K lines. These filters together produced 280 candidate stars to be vetted manually.

The vetting process was done through visual examination of each case. The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing. The local noisiness of the signal was taken into account when making these determinations. Of the 280 candidates manually vetted, 156 were ultimately determined to be sufficiently strong candidates to make the list, presented in Table [INSERT TABLE REFERENCE HERE].

>>>>

This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed. 190 strong candidates for this signature, almost all of them not at this time associated with any globular cluster, are detailed in Table [REFERENCE TABLE HERE]. These stars occur at a wide range of metalicities, including solar metalicity. The implications for theories attempting to explain the origin of this signiature first found in NGC 2419 is likely to be significant, as for such a theory to be complete, it must now account not only for the stars in the metal poor NGC 2419, but also these stars existing at a range of metalicities in the galactic plane. Further, the task of explaining the uniqueness of NGC 2419 is not removed, as it remains the only globular cluster to significantly display this phenomena.

@@

The data set of 454180 LAMOST giants was prepared by \citet{ho2017} for use with the supervised machine learning code \textit{The Cannon}. The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA and 9000 \AA. \textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey, through the use of a data-driven spectral model, referred to henceforth and simply 'the model'. For details regarding the process of the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}. The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.

Residuals were taken of the normalised LAMOST flux data and 
\textit{The Cannon} according to $residual=data-model$. A positive residual therefore implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected. In turn, at a given spectral line a lower normalised flux is associated with an over-abundance, while a higher normalised flux is associated with a depleted abundance.

@@

Three filters were applied separately, with the candidate pool formed from all unique stars identified any of the three filters. The first filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$. The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the two K lines to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$. The third filter removed the amplitude requirement to requiring only positivity on 2/3 Mg lines and negativity on \textit{both} K lines, in addition to data quality requirements $\chi^2<3$ and $S/N>30$
These filters together produced 384 unique candidate stars to be vetted manually.

The vetting process was done through visual examination of each case. The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing. The apparent noisiness of the signal was qualitatively taken into account when making these determinations. Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong candidates to be worth reporting in Table [INSERT TABLE REFERENCE HERE].
